\bf Title here

### 2020-06-23 paper/paper.Rmd
fix typo

Derivative free methods provides another option to optimise the objective function without evaluating any gradient or hessian information and a parciular class of methods: direct search, has gained its popularity through its conceptual simplicity.  However, the whole searching process in the algorithm remains a black-box. Plots are usually used to evaluate and compare the performance of different algorithms but it can easily become tedious because the code will have to be modified significantly when comparing different parameters in the algorithms. For example, a categorical variable with 5 levels can be easily mapped onto color while mapping another categorical variable with 30 levels will not make the plot informative. Thus the plot needs to be re-designed to better suits the characteristics of the parameter (whether the parameter is a scalar or a matrix? whether the parameter is quantitative or categorical? If categorical, how many levels does the parameter have?). This motivates the  design of a visual diagnostic framework for optimisation algorithms based on the idea of a *global object*.

The paper is organised as follows. Section \ref{DFO} gives a general literature review of optimisation, specifically derivative free optimisation. Section \ref{vis-diag} presents the new idea of constructing a
systematic visual framework that diagnoses the components of an optimisation procedure (parameters, searching path, etc). The rest of the paper serves as a comprehensive example of using the visual diagnostics on one particular problem: *projection pursuit guided tour*. Some background knowledge of projection pursuit guided tour is provided in Section \ref{tour}. Section \ref{apply} applys the concepts proposed in section \ref{vis-diag} in the tour problem and sets up the data. The last section, Section \ref{plots}, presents the visual diagnostic plots and explains how they can help to understand different aspects of the optimisation in tour.

@@

[Are we using  projection pursuit/guided tour to better understand the convergency of optimization algorithms visually in combination with the algorithms discussed below? Or we are focusing on the optimisation problem only within the project pursuit context? Some of the problems listed below are also applicable to optimization problem in general too. ppp]

@@

[I would expland this section more as the core contribution. ppp]

>>>>

Derivative free methods provides another option to optimise the objective function without evaluating any gradient or Hessian information and a particular class of methods: direct search, has gained its popularity through its conceptual simplicity.  However, the whole searching process in the algorithm remains a black-box. Plots are usually used to evaluate and compare the performance of different algorithms but it can easily become tedious because the code will have to be modified significantly when comparing different parameters in the algorithms. For example, a categorical variable with 5 levels can be easily mapped onto color while mapping another categorical variable with 30 levels will not make the plot informative. Thus the plot needs to be re-designed to better suits the characteristics of the parameter (whether the parameter is a scalar or a matrix? whether the parameter is quantitative or categorical? If categorical, how many levels does the parameter have?). This motivates the  design of a visual diagnostic framework for optimisation algorithms based on the idea of a *global object*.

The paper is organised as follows. Section \ref{DFO} gives a general literature review of optimisation, specifically derivative free optimisation. Section \ref{vis-diag} presents the new idea of constructing a
systematic visual framework that diagnoses the components of an optimisation procedure (parameters, searching path, etc). The rest of the paper serves as a comprehensive example of using the visual diagnostics on one particular problem: *projection pursuit guided tour*. Some background knowledge of projection pursuit guided tour is provided in Section \ref{tour}. Section \ref{apply} applies the concepts proposed in section \ref{vis-diag} in the tour problem and sets up the data. The last section, Section \ref{plots}, presents the visual diagnostic plots and explains how they can help to understand different aspects of the optimisation in tour.

@@

[Are we using  projection pursuit/guided tour to better understand the convergence of optimization algorithms visually in combination with the algorithms discussed below? Or we are focusing on the optimisation problem only within the project pursuit context? Some of the problems listed below are also applicable to optimization problem in general too. ppp]

@@

[I would expand this section more as the core contribution. ppp]

### 2020-06-23 paper/paper.tex
fix typo

Derivative free methods provides another option to optimise the
objective function without evaluating any gradient or hessian
information and a parciular class of methods: direct search, has gained
its popularity through its conceptual simplicity. However, the whole
searching process in the algorithm remains a black-box. Plots are
usually used to evaluate and compare the performance of different
algorithms but it can easily become tedious because the code will have
to be modified significantly when comparing different parameters in the
algorithms. For example, a categorical variable with 5 levels can be
easily mapped onto color while mapping another categorical variable with
30 levels will not make the plot informative. Thus the plot needs to be
re-designed to better suits the characteristics of the parameter
(whether the parameter is a scalar or a matrix? whether the parameter is
quantitative or categorical? If categorical, how many levels does the
parameter have?). This motivates the design of a visual diagnostic
framework for optimisation algorithms based on the idea of a
\emph{global object}.

The paper is organised as follows. Section \ref{DFO} gives a general
literature review of optimisation, specifically derivative free
optimisation. Section \ref{vis-diag} presents the new idea of
constructing a systematic visual framework that diagnoses the components
of an optimisation procedure (parameters, searching path, etc). The rest
of the paper serves as a comprehensive example of using the visual
diagnostics on one particular problem: \emph{projection pursuit guided
tour}. Some background knowledge of projection pursuit guided tour is
provided in Section \ref{tour}. Section \ref{apply} applys the concepts
proposed in section \ref{vis-diag} in the tour problem and sets up the
data. The last section, Section \ref{plots}, presents the visual
diagnostic plots and explains how they can help to understand different
aspects of the optimisation in tour.

@@

{[}Are we using projection pursuit/guided tour to better understand the
convergency of optimization algorithms visually in combination with the
algorithms discussed below? Or we are focusing on the optimisation
problem only within the project pursuit context? Some of the problems
listed below are also applicable to optimization problem in general too.
ppp{]}

@@

{[}I would expland this section more as the core contribution. ppp{]}

>>>>

Derivative free methods provides another option to optimise the
objective function without evaluating any gradient or Hessian
information and a particular class of methods: direct search, has gained
its popularity through its conceptual simplicity. However, the whole
searching process in the algorithm remains a black-box. Plots are
usually used to evaluate and compare the performance of different
algorithms but it can easily become tedious because the code will have
to be modified significantly when comparing different parameters in the
algorithms. For example, a categorical variable with 5 levels can be
easily mapped onto color while mapping another categorical variable with
30 levels will not make the plot informative. Thus the plot needs to be
re-designed to better suits the characteristics of the parameter
(whether the parameter is a scalar or a matrix? whether the parameter is
quantitative or categorical? If categorical, how many levels does the
parameter have?). This motivates the design of a visual diagnostic
framework for optimisation algorithms based on the idea of a
\emph{global object}.

The paper is organised as follows. Section \ref{DFO} gives a general
literature review of optimisation, specifically derivative free
optimisation. Section \ref{vis-diag} presents the new idea of
constructing a systematic visual framework that diagnoses the components
of an optimisation procedure (parameters, searching path, etc). The rest
of the paper serves as a comprehensive example of using the visual
diagnostics on one particular problem: \emph{projection pursuit guided
tour}. Some background knowledge of projection pursuit guided tour is
provided in Section \ref{tour}. Section \ref{apply} applies the concepts
proposed in section \ref{vis-diag} in the tour problem and sets up the
data. The last section, Section \ref{plots}, presents the visual
diagnostic plots and explains how they can help to understand different
aspects of the optimisation in tour.

@@

{[}Are we using projection pursuit/guided tour to better understand the
convergence of optimization algorithms visually in combination with the
algorithms discussed below? Or we are focusing on the optimisation
problem only within the project pursuit context? Some of the problems
listed below are also applicable to optimization problem in general too.
ppp{]}

@@

{[}I would expand this section more as the core contribution. ppp{]}
